---
title: "newton"
author: "YunranChen"
date: "5/10/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("statmod")
library("statmod")
library(purrr)
library(dplyr)
library(magrittr)
library(ggplot2)
library(tidyr)
theme_set(theme_bw())
#install.packages("truncdist")
library(truncdist)
library(rbenchmark)
rm(list=ls())
```

## decide the range for x according to rule-of-thumb

```{r}
x_range=function(xs_vec,ntheta,l,u){
  n=length(xs_vec)
  bw_cut=sd(xs_vec)*(4/3/n)^(1/5)*3
  ub=max(xs_vec)+bw_cut
  lb=min(xs_vec)-bw_cut
  xxs=seq(max(lb,l),min(ub,u),length.out = ntheta)
  return(xxs)
}
```

## GP mixture

### truncated gamma

```{r}
rtgamma=function(size,shape_,rate_,a,b){
  u=runif(n = size)
  c_inv=pgamma(q = b,shape = shape_,rate = rate_)-pgamma(q = a,shape = shape_,rate = rate_)
  x=qgamma(p = u*c_inv+pgamma(q=a,shape=shape_,rate=rate_),shape=shape_,rate = rate_)
  return(x)
}
dtgamma=function(x_,shape_,rate_,a,b){
  c_inv=pgamma(q = b,shape = shape_,rate = rate_)-pgamma(q = a,shape = shape_,rate = rate_)
  x=dgamma(x = x_,shape=shape_,rate = rate_)/c_inv
  return(x)
}
```

```{r}
##test my function
set.seed(123)
rtgamma(100000,2,0.4,0,10)%>%density(.)%>%plot(.)
set.seed(123)
rtrunc(n = 100000,spec = "gamma",a=0,b=10,shape=2,rate=0.4)%>%density(.)%>%plot(.)

dtrunc(x  = 1:10,spec = "gamma",a = 0,b = 10,shape=2,rate=0.4)
dtgamma(x_ = 1:10,shape_ = 2,rate_=0.4,0,10)

```

# (1) truncated gamma -- possion

## Data Preparation

```{r}

## try poisson + truncated-gamma mixture
N=100 #size for sample
n=200 #size for each sample
set.seed(123)
gp_sampler_=function(size_){
  xs_g=rtgamma(size =  size_,shape_ = 2,rate_ = 0.4,a = 0,b=10)
  xs_gp=map_dbl(xs_g,~rpois(n = 1,lambda = .x))
return(xs_gp)
}
Xs_bn=sapply(1:N,function(x){gp_sampler_(n)})%>%t()
```


## Predictive Recursive

```{r}
PR_GP=function(Xs_bn,a,b,nGQ,ntheta){

N=nrow(Xs_bn)
#guass.quad
out=gauss.quad(nGQ)
xs_gq=out$nodes*(b-a)/2+(a+b)/2 #change interval
theta=seq(a,b,length.out = ntheta)

## Initial Guess: Uniform on [0,50]
p=rep(1/(b-a),ntheta) #notice these points correspond to the xs

## weight seq
w=1/(1:n+1)

##Recursion
pr=function(i,p_0){
  p=p_0
for (j in 1:n){
  p_x=map_dbl(theta,~dpois(x = Xs_bn[i,j],lambda = .x))
  p=(1-w[j])*p+w[j]*p_x*p/((b-a)/2*sum(out$weights*map_dbl(xs_gq,~dpois(x = Xs_bn[i,j],lambda = .x))*p[ceiling(xs_gq/((b-a)/ntheta))]))
}
  return(p)
}
res=sapply(1:N,function(i){return(pr(i,p))})

##draw f(theta)
colnames(res)=paste0("est",1:N)
ggdf=res%>%as_tibble()%>%
  mutate(x=theta,true=dtgamma(x_ = theta,shape_ = 2,rate_=0.4,a = a,b=b))%>%
  gather(data = .,key=estimation,value=p,-x)
plotme_f=ggplot(data=ggdf,mapping = aes(x=x,y=p,group=estimation))+geom_line(colour = "grey",alpha=0.7)+geom_line(data=ggdf%>%filter(estimation=="true"),mapping = aes(x=x,y=p))+ggtitle("Gamma(2,0.4)[0,10]+Poisson")


## get the p(x) -- Using Guassian Quadratic

Xss=apply(Xs_bn, 1, function(x){x_range(xs_vec = x,ntheta = ntheta,l = 0,u = Inf)})

xs=sapply(1:ntheta,function(j){
  map_dbl(.x = Xss[,j],.f = function(xs_j){(b-a)/2*sum(out$weights*map_dbl(xs_gq,~dpois(x=round(xs_j),lambda = .x))*res[,j][ceiling(xs_gq/((b-a)/ntheta))])})
})

true_xs=x_range(xs_vec = as.vector(Xs_bn),ntheta = ntheta,l = 0,u = Inf)
true=map_dbl(.x = true_xs,
             .f =function(xxs_i){ (b-a)/2*sum(out$weights*map_dbl(xs_gq,~dpois(x = round(xxs_i),lambda = .x))*(dtgamma(x_ = theta,shape_ = 2,rate_ = 0.4,a = a,b = b))[ceiling(xs_gq/((b-a)/ntheta))])})

ggdf_p=data_frame(x=c(as.vector(Xss),true_xs)%>%round(.),p=c(as.vector(xs),true),estimation=c(paste0("est",rep(1:N,each=ntheta)),rep("true",ntheta)))
plotme_p=ggplot(data=ggdf_p,mapping = aes(x=x,y=p,group=estimation))+geom_line(colour = "grey",alpha=0.7)+geom_line(data=ggdf_p%>%filter(estimation=="true"),mapping = aes(x=x,y=p))+ggtitle("Gamma(2,0.4)[0,10]+Poisson")

print(plotme_f)
print(plotme_p)
}
```

```{r}
tic=proc.time()
PR_GP(Xs_bn=Xs_bn,a=0,b=10,nGQ=20,ntheta=100)
toc=proc.time()
toc-tic
#robust. no need to set.seed
```

## Permutation Version PPR

```{r}
PPR_GP=function(Xs_bn,a,b,nGQ,ntheta){
#permutation
N=nrow(Xs_bn)
n=ncol(Xs_bn)
nP=100
ind=sapply(1:nP,function(x){sample.int(n = n,size = n,replace = FALSE)})

#guass.quad
out=gauss.quad(nGQ)
xs_gq=out$nodes*(b-a)/2+(a+b)/2 #change interval
theta=seq(a,b,length.out = ntheta)

## Initial Guess: Uniform on [0,10]
p=rep(1/(b-a),ntheta) #notice these points correspond to the xs

## weight seq
w=1/(1:n+1)

##Recursion
ppr=function(i,p_0,Xs_bn){
  p=p_0
  xs_bn=Xs_bn[i,]
  Xs_bn_p=sapply(1:nP,function(i){xs_bn[ind[,i]]})

  pp=sapply(1:nP,function(ix){
    for (j in 1:n){
      p_x=map_dbl(theta,~dpois(x = Xs_bn_p[j,ix],lambda = .x))
      p=(1-w[j])*p+w[j]*p_x*p/((b-a)/2*sum(out$weights*map_dbl(xs_gq,~dpois(x = Xs_bn_p[j,ix],lambda = .x))*p[ceiling(xs_gq/((b-a)/ntheta))]))
    }
    return(p)
  })%>%apply(., 1,mean)
  return(pp)
}

res=sapply(1:N,function(i){return(ppr(i,p,Xs_bn))})

##draw f(theta)
colnames(res)=paste0("est",1:N)
ggdf=res%>%as_tibble()%>%
  mutate(x=theta,true=dtgamma(x_ = theta,shape_ = 2,rate_=0.4,a = a,b=b))%>%
  gather(data = .,key=estimation,value=p,-x)
plotme_f=ggplot(data=ggdf,mapping = aes(x=x,y=p,group=estimation))+geom_line(colour = "grey",alpha=0.7)+geom_line(data=ggdf%>%filter(estimation=="true"),mapping = aes(x=x,y=p))+ggtitle("Gamma(2,0.4)[0,10]+Poisson")


## get the p(x) -- Using Guassian Quadratic

Xss=apply(Xs_bn, 1, function(x){x_range(xs_vec = x,ntheta = ntheta,l = 0,u = Inf)})

xs=sapply(1:ntheta,function(j){
  map_dbl(.x = Xss[,j],.f = function(xs_j){(b-a)/2*sum(out$weights*map_dbl(xs_gq,~dpois(x=round(xs_j),lambda = .x))*res[,j][ceiling(xs_gq/((b-a)/ntheta))])})
})

true_xs=x_range(xs_vec = as.vector(Xs_bn),ntheta = ntheta,l = 0,u = Inf)
true=map_dbl(.x = true_xs,
             .f =function(xxs_i){ (b-a)/2*sum(out$weights*map_dbl(xs_gq,~dpois(x = round(xxs_i),lambda = .x))*(dtgamma(x_ = theta,shape_ = 2,rate_ = 0.4,a = a,b = b))[ceiling(xs_gq/((b-a)/ntheta))])})

ggdf_p=data_frame(x=c(as.vector(Xss),true_xs)%>%round(.),p=c(as.vector(xs),true),estimation=c(paste0("est",rep(1:N,each=ntheta)),rep("true",ntheta)))
plotme_p=ggplot(data=ggdf_p,mapping = aes(x=x,y=p,group=estimation))+geom_line(colour = "grey",alpha=0.7)+geom_line(data=ggdf_p%>%filter(estimation=="true"),mapping = aes(x=x,y=p))+ggtitle("Gamma(2,0.4)[0,10]+Poisson")

print(plotme_f)
print(plotme_p)
}
```

```{r}
tic=proc.time()
PPR_GP(Xs_bn=Xs_bn,a=0,b=10,nGQ=20,ntheta=100)
toc=proc.time()
toc-tic
```


## Comparision between GQ and sampling

```{r}
PR_BN_mix=function(Xs_bn,a,b,nGQ,ntheta){
  N=nrow(Xs_bn)
#guass.quad
out=gauss.quad(nGQ)
xs_gq=out$nodes*(b-a)/2+(a+b)/2 #change interval
theta=seq(a,b,length.out = ntheta)

## Initial Guess: Uniform on [0,1]
p=rep(1/(b-a),ntheta) #notice these points correspond to the xs

## weight seq
w=1/(1:n+1)

##Recursion
pr=function(i,p_0){
  p=p_0
for (j in 1:n){
  p_x=map_dbl(theta,~dnorm(x = Xs_bn[i,j],mean = .x,sd = sigma))
  p=(1-w[j])*p+w[j]*p_x*p/((b-a)/2*sum(out$weights*map_dbl(xs_gq,~dnorm(Xs_bn[i,j],.x,sigma))*p[ceiling(xs_gq/(1/ntheta))]))
}
  return(p)
}
res=sapply(1:N,function(i){return(pr(i,p))})
colnames(res)=paste0("est",1:N)

##draw f(theta)

ggdf=res%>%as_tibble()%>%mutate(x=theta,true=1/3*dbeta(theta,3,30)+2/3*dbeta(theta,4,4))%>%gather(data = .,key=estimation,value=p,-x)
plotme_f=ggplot(data=ggdf,mapping = aes(x=x,y=p,group=estimation))+geom_line(colour = "grey",alpha=0.7)+geom_line(data=ggdf%>%filter(estimation=="true"),mapping = aes(x=x,y=p))+ggtitle("1/3Beta(3,30)+2/3Beta(4,4)+Normal(,0.1)")

## get the p(x) 

###Using sampling 
sampling=function(){
  m=1500
res_norm=t(t(res)/apply(res,2,sum))
thetas=sapply(1:N, function(x){
  sample(x = theta,size = m,replace = TRUE,prob = res_norm[,x])
})

xs=sapply(1:N,function(j){
  map_dbl(1:m,~rnorm(n = 1,mean = thetas[.x,j],sd = sigma))
})
colnames(xs)=paste0("est",1:N)
  components = sample(1:2,prob=c(1/3,2/3),size=m,replace=TRUE)
  shape1_=c(3,4)
  shape2_=c(30,4)
  true_pis=map_dbl(components,~rbeta(n = 1,shape1 = shape1_[.x],shape2=shape2_[.x] ))
  
ggdf=xs%>%as_tibble()%>%mutate(true=map_dbl(1:m,~rnorm(n = 1,mean = true_pis[.x],sd = sigma)))%>%
  gather(data = .,key=estimation,value=xs)
plotme_p=ggplot(data=ggdf,mapping = aes(x=xs,group=estimation))+geom_density(colour = "grey",alpha=0.7)+geom_density(data=ggdf%>%filter(estimation=="true"),mapping = aes(x=xs))
#print(plotme_p)
}
###Using Guassian Quadratic
gq=function(){

Xss=apply(Xs_bn, 1, function(x){x_range(xs_vec = x,ntheta = ntheta)})
xs=sapply(1:ntheta,function(j){
  map_dbl(.x = Xss[,j],.f = function(xs_j){(b-a)/2*sum(out$weights*map_dbl(xs_gq,~dnorm(xs_j,.x,sigma))*res[,j][ceiling(xs_gq/(1/ntheta))])})
})

colnames(xs)=paste0("est",1:N)

true=map_dbl(.x = x_range(xs_vec = as.vector(Xs_bn),ntheta = ntheta),.f =function(xxs_i){ (b-a)/2*sum(out$weights*map_dbl(xs_gq,~dnorm(xxs_i,.x,sigma))*(1/3*dbeta(theta,3,30)+2/3*dbeta(theta,4,4))[ceiling(xs_gq/(1/ntheta))])})

ggdf_p=xs%>%as_tibble()%>%mutate(x=xxs,true=true)%>%gather(data = .,key=estimation,value=p,-x)
plotme_p=ggplot(data=ggdf_p,mapping = aes(x=x,y=p,group=estimation))+geom_line(colour = "grey",alpha=0.7)+geom_line(data=ggdf_p%>%filter(estimation=="true"),mapping = aes(x=x,y=p))+ggtitle("1/3Beta(3,30)+2/3Beta(4,4)+Normal(,0.1)")
}
print(plotme_f)
print(plotme_p)
}
plotme_p2=plotme_p
print(plotme_p)
print(plotme_p2)
print(plotme_p1)
benchmark(
  gq(),
  sampling(),
  replications = 10
)
```

# (2) truncated gamma + point mass mixture -- possion

$f(\theta) = \frac{1}{2}\delta_{10}+\frac{1}{2}Gamma_{[0,10]}(2,0.4)$

## Data Preparation

```{r}

## try truncated gamma + point mass mixture -- possion
N=100 #size for sample
n=200 #size for each sample
set.seed(123)

gpp_sampler_=function(size_){
  xs_g=vector(length = size_)
  components = sample(1:2,prob=c(1/2,1/2),size=size_,replace=TRUE)
  xs_g[components==1]=10
  xs_g[components==2]=rtgamma(size =  sum(components==2),shape_ = 2,rate_ = 0.4,a = 0,b=10)
  xs_gp=map_dbl(xs_g,~rpois(n = 1,lambda = .x))
return(xs_gp)
}
Xs_bn=sapply(1:N,function(x){gpp_sampler_(n)})%>%t()
#Each row is a sample
```

## Predictive Recursive

```{r}
PR_GPP=function(Xs_bn,a,b,theta0,nGQ,ntheta){

N=nrow(Xs_bn)
n=ncol(Xs_bn)
#guass.quad
out=gauss.quad(nGQ)
xs_gq=out$nodes*(b-a)/2+(a+b)/2 #change interval
theta=seq(a,b,length.out = ntheta)

## Initial Guess: Uniform on [0,10]

p=rep(1/(b-a)/2,ntheta) #uniform
#p=dbeta(x = seq(0,1,length.out = ntheta),shape1 = c,shape2 = c)/(b-a)/2
ind0=ceiling((theta0-a)/((b-a)/ntheta))
p[ind0]=1/2

## weight seq
w=1/(1:n+1)

##Recursion
pr=function(i,p_0){
  p=p_0
for (j in 1:n){
  p_x=map_dbl(theta,~dpois(x = Xs_bn[i,j],lambda = .x))
  int=((b-a)/2*sum(out$weights*map_dbl(xs_gq,~dpois(x = Xs_bn[i,j],lambda = .x))*p[ceiling((xs_gq-a)/((b-a)/ntheta))]))*(1-p[ind0])+p[ind0]*dpois(x = Xs_bn[i,j],lambda = theta0)
  p=(1-w[j])*p+w[j]*p_x*p/int
}
  return(p)
}
res=sapply(1:N,function(i){return(pr(i,p))})

##draw f(theta)
colnames(res)=paste0("est",1:N)
true_f=dtgamma(x_ = theta,shape_ = 2,rate_=0.4,a = a,b=b)*0.5
true_f[ind0]=0.5
res_f=res
for (col in 1:ncol(res)){
  res_f[-ind0,col]=(1-res[ind0,col])*res[-ind0,col]
}
ggdf=res_f%>%as_tibble()%>%
  mutate(x=theta,true=true_f)%>%
  gather(data = .,key=estimation,value=p,-x)
plotme_f=ggplot(data=ggdf,mapping = aes(x=x,y=p,group=estimation))+geom_line(colour = "grey",alpha=0.7)+geom_line(data=ggdf%>%filter(estimation=="true"),mapping = aes(x=x,y=p))+ggtitle(paste0("Gamma(2,0.4)[0,10]+Delta_10+Poisson_",ntheta))##+ggtitle("Gamma(2,0.4)[0,10]+Delta_10+Poisson")#


## get the p(x) -- Using Guassian Quadratic

Xss=apply(Xs_bn, 1, function(x){x_range(xs_vec = x,ntheta = ntheta,l = 0,u = Inf)})

xs=sapply(1:N,function(j){
  map_dbl(.x = Xss[,j],.f = function(xs_j){
    (b-a)/2*sum(out$weights*map_dbl(xs_gq,~dpois(x=round(xs_j),lambda = .x))*res[,j][ceiling((xs_gq-a)/((b-a)/ntheta))])*(1-res[,j][ind0])+res[,j][ind0]*dpois(x = round(xs_j),lambda = theta0)
  })
  
})

true_xs=x_range(xs_vec = as.vector(Xs_bn),ntheta = ntheta,l = 0,u = Inf)
true=map_dbl(.x = true_xs,
             .f =function(xxs_i){ p=(b-a)/2*sum(out$weights*map_dbl(xs_gq,~dpois(x = round(xxs_i),lambda = .x))*(dtgamma(x_ = theta,shape_ = 2,rate_ = 0.4,a = a,b = b))[ceiling((xs_gq-a)/((b-a)/ntheta))])*0.5+0.5*dpois(x = round(xxs_i),lambda = theta0)
             })

ggdf_p=data_frame(x=c(as.vector(Xss),true_xs)%>%round(.),p=c(as.vector(xs),true),estimation=c(paste0("est",rep(1:N,each=ntheta)),rep("true",ntheta)))
plotme_p=ggplot(data=ggdf_p,mapping = aes(x=x,y=p,group=estimation))+geom_line(colour = "grey",alpha=0.7)+geom_line(data=ggdf_p%>%filter(estimation=="true"),mapping = aes(x=x,y=p))+ggtitle(paste0("Gamma(2,0.4)[0,10]+Delta_10+Poisson_",ntheta))#+ggtitle("Gamma(2,0.4)[0,10]+Delta_10+Poisson")

#print(plotme_f)
#print(plotme_p)
return(list(result=res[ind0,],f=plotme_f,p=plotme_p))
}
```

```{r}
tic=proc.time()
for (c in c(1.1,1.5,2,4,8)){
  print(paste0("beta(",c,")"))
  pi_=PR_GPP(Xs_bn=Xs_bn,a=0,b=10,c=c,theta0 = 10,nGQ=20,ntheta=100)
  print(pi_%>%summary(.))
  print((pi_<0.5)%>%mean)
  hist(pi_)
}

toc=proc.time()
toc-tic

pi_=PR_GPP(Xs_bn=Xs_bn,a=0,b=10,c=4,theta0 = 10,nGQ=20,ntheta=100)
print(pi_%>%summary(.))
print((pi_<0.5)%>%mean)
hist(pi_)

#
for (grids in c(100,500,1000,1500,2000)){
  print(paste0("ntheta(",grids,")"))
  pi_=PR_GPP(Xs_bn=Xs_bn,a=0,b=10,theta0 = 10,nGQ=20,ntheta=grids)
  #print(pi_$p)
  #print(pi_$f)
  print(pi_$result%>%summary(.))
  print((pi_$result<0.5)%>%mean)
  hist(pi_$result)
}
```




## Permutation Version PPR

```{r}
PPR_GPP=function(Xs_bn,a,b,c,theta0,nGQ,ntheta){

#permutation
N=nrow(Xs_bn)
n=ncol(Xs_bn)
nP=100
ind=sapply(1:nP,function(x){sample.int(n = n,size = n,replace = FALSE)})

#guass.quad
out=gauss.quad(nGQ)
xs_gq=out$nodes*(b-a)/2+(a+b)/2 #change interval
theta=seq(a,b,length.out = ntheta)

## Initial Guess: Uniform on [0,10]
#p=rep(1/(b-a)/2,ntheta)
p=dbeta(x = seq(0,1,length.out = ntheta),shape1 = c,shape2 = c)/(b-a)/2
ind0=ceiling((theta0-a)/((b-a)/ntheta))
p[ind0]=1/2
## weight seq
w=1/(1:n+1)

##Recursion
ppr=function(i,p_0,Xs_bn){
  p=p_0
  xs_bn=Xs_bn[i,]
  Xs_bn_p=sapply(1:nP,function(i){xs_bn[ind[,i]]})

  pp=sapply(1:nP,function(ix){
    for (j in 1:n){
      p_x=map_dbl(theta,~dpois(x = Xs_bn_p[j,ix],lambda = .x))
      int=((b-a)/2*sum(out$weights*map_dbl(xs_gq,~dpois(x = Xs_bn_p[j,ix],lambda = .x))*p[ceiling((xs_gq-a)/((b-a)/ntheta))])*(1-p[ind0]))+p[ind0]*dpois(x = Xs_bn_p[j,ix],lambda = theta0)
  p=(1-w[j])*p+w[j]*p_x*p/int

    }
    return(p)
  })%>%apply(., 1,mean)
  return(pp)
}

res=sapply(1:N,function(i){return(ppr(i,p,Xs_bn))})

##draw f(theta)
colnames(res)=paste0("est",1:N)
true_f=dtgamma(x_ = theta,shape_ = 2,rate_=0.4,a = a,b=b)*0.5
true_f[ind0]=0.5
res_f=res
for (col in 1:ncol(res)){
  res_f[-ind0,col]=(1-res[ind0,col])*res[-ind0,col]
}
ggdf=res_f%>%as_tibble()%>%
  mutate(x=theta,true=true_f)%>%
  gather(data = .,key=estimation,value=p,-x)
plotme_f=ggplot(data=ggdf,mapping = aes(x=x,y=p,group=estimation))+geom_line(colour = "grey",alpha=0.7)+geom_line(data=ggdf%>%filter(estimation=="true"),mapping = aes(x=x,y=p))+ggtitle(paste0("Gamma(2,0.4)[0,10]+Delta_10+Poisson_",c))#+ggtitle("Gamma(2,0.4)[0,10]+Delta_10+Poisson")


## get the p(x) -- Using Guassian Quadratic

Xss=apply(Xs_bn, 1, function(x){x_range(xs_vec = x,ntheta = ntheta,l = 0,u = Inf)})

xs=sapply(1:ntheta,function(j){
  map_dbl(.x = Xss[,j],.f = function(xs_j){
    (b-a)/2*sum(out$weights*map_dbl(xs_gq,~dpois(x=round(xs_j),lambda = .x))*res[,j][ceiling((xs_gq-a)/((b-a)/ntheta))])*(1-res[,j][ind0])+res[,j][ind0]*dpois(x = round(xs_j),lambda = theta0)
  })
  
})

true_xs=x_range(xs_vec = as.vector(Xs_bn),ntheta = ntheta,l = 0,u = Inf)
true=map_dbl(.x = true_xs,
             .f =function(xxs_i){ p=(b-a)/2*sum(out$weights*map_dbl(xs_gq,~dpois(x = round(xxs_i),lambda = .x))*(dtgamma(x_ = theta,shape_ = 2,rate_ = 0.4,a = a,b = b))[ceiling((xs_gq-a)/((b-a)/ntheta))])*0.5+0.5*dpois(x = round(xxs_i),lambda = theta0)
             })

ggdf_p=data_frame(x=c(as.vector(Xss),true_xs)%>%round(.),p=c(as.vector(xs),true),estimation=c(paste0("est",rep(1:N,each=ntheta)),rep("true",ntheta)))
plotme_p=ggplot(data=ggdf_p,mapping = aes(x=x,y=p,group=estimation))+geom_line(colour = "grey",alpha=0.7)+geom_line(data=ggdf_p%>%filter(estimation=="true"),mapping = aes(x=x,y=p))+ggtitle(paste0("Gamma(2,0.4)[0,10]+Delta_10+Poisson_",c))#+ggtitle("Gamma(2,0.4)[0,10]+Delta_10+Poisson")

print(plotme_f)
print(plotme_p)
return(res[ind0,])
}
```

```{r}
tic=proc.time()
pi__=PPR_GPP(Xs_bn=Xs_bn,a=0,b=10,c=4,theta0 = 10,nGQ=20,ntheta=100)
toc=proc.time()
toc-tic
print(pi__%>%summary(.))
print((pi__<0.5)%>%mean)
hist(pi__)
```

# (3) truncated gamma + 2 point mass mixture -- possion

$f(\theta) = \frac{1}{2}\delta_{10}+\frac{1}{2}Gamma_{[0,10]}(2,0.4)$

## Data Preparation

```{r}

## try truncated gamma + point mass mixture -- possion
N=100 #size for sample
n=200 #size for each sample
set.seed(123)

gpp_sampler_=function(size_){
  xs_g=vector(length = size_)
  components = sample(1:3,prob=c(0.25,0.5,0.25),size=size_,replace=TRUE)
  xs_g[components==1]=0
  xs_g[components==3]=10
  xs_g[components==2]=rtgamma(size =  sum(components==2),shape_ = 2,rate_ = 0.4,a = 0,b=10)
  xs_gp=map_dbl(xs_g,~rpois(n = 1,lambda = .x))
return(xs_gp)
}
Xs_bn=sapply(1:N,function(x){gpp_sampler_(n)})%>%t()
#Each row is a sample
```

## Predictive Recursive

```{r}
PR_GP2P=function(Xs_bn,a,b,theta0,nGQ,ntheta){

N=nrow(Xs_bn)
#guass.quad
out=gauss.quad(nGQ)
xs_gq=out$nodes*(b-a)/2+(a+b)/2 #change interval
theta=seq(a,b,length.out = ntheta)

## Initial Guess: Uniform on [0,10]

p=rep(1/(b-a)/2,ntheta) #uniform
#p=dbeta(x = seq(0,1,length.out = ntheta),shape1 = c,shape2 = c)/(b-a)/2
inds=ceiling((theta0-a)/((b-a)/ntheta))
p[inds]=c(0.25,0.25)

## weight seq
w=1/(1:n+1)

##Recursion
pr=function(i,p_0){
  p=p_0
for (j in 1:n){
  p_x=map_dbl(theta,~dpois(x = Xs_bn[i,j],lambda = .x))
  int=((b-a)/2*sum(out$weights*map_dbl(xs_gq,~dpois(x = Xs_bn[i,j],lambda = .x))*p[ceiling((xs_gq-a)/((b-a)/ntheta))]))*(1-sum(p[inds]))+p[inds[1]]*dpois(x = Xs_bn[i,j],lambda = theta0[1])+p[inds[2]]*dpois(x = Xs_bn[i,j],lambda = theta0[2])
  p=(1-w[j])*p+w[j]*p_x*p/int
}
  return(p)
}
res=sapply(1:N,function(i){return(pr(i,p))})

##draw f(theta)
colnames(res)=paste0("est",1:N)
true_f=dtgamma(x_ = theta,shape_ = 2,rate_=0.4,a = a,b=b)*0.5
true_f[inds]=c(0.25,0.25)
res_f=res
for (col in 1:ncol(res)){
  res_f[-inds,col]=(1-sum(res[inds,col]))*res[-inds,col]
}
ggdf=res_f%>%as_tibble()%>%
  mutate(x=theta,true=true_f)%>%
  gather(data = .,key=estimation,value=p,-x)
plotme_f=ggplot(data=ggdf,mapping = aes(x=x,y=p,group=estimation))+geom_line(colour = "grey",alpha=0.7)+geom_line(data=ggdf%>%filter(estimation=="true"),mapping = aes(x=x,y=p))+ggtitle("Gamma(2,0.4)[0,10]+Delta_10,0+Poisson")


## get the p(x) -- Using Guassian Quadratic

Xss=apply(Xs_bn, 1, function(x){x_range(xs_vec = x,ntheta = ntheta,l = 0,u = Inf)})

xs=sapply(1:ntheta,function(j){
  map_dbl(.x = Xss[,j],.f = function(xs_j){
    (b-a)/2*sum(out$weights*map_dbl(xs_gq,~dpois(x=round(xs_j),lambda = .x))*res[,j][ceiling((xs_gq-a)/((b-a)/ntheta))])*(1-sum(res[,j][inds]))+res[,j][inds[1]]*dpois(x = round(xs_j),lambda = theta0[1])+res[,j][inds[2]]*dpois(x = round(xs_j),lambda = theta0[2])
  })
  
})

true_xs=x_range(xs_vec = as.vector(Xs_bn),ntheta = ntheta,l = 0,u = Inf)
true=map_dbl(.x = true_xs,
             .f =function(xxs_i){ p=(b-a)/2*sum(out$weights*map_dbl(xs_gq,~dpois(x = round(xxs_i),lambda = .x))*(dtgamma(x_ = theta,shape_ = 2,rate_ = 0.4,a = a,b = b))[ceiling((xs_gq-a)/((b-a)/ntheta))])*0.5+0.25*dpois(x = round(xxs_i),lambda = theta0[1])+0.25*dpois(x = round(xxs_i),lambda = theta0[2])
             })

ggdf_p=data_frame(x=c(as.vector(Xss),true_xs)%>%round(.),p=c(as.vector(xs),true),estimation=c(paste0("est",rep(1:N,each=ntheta)),rep("true",ntheta)))
plotme_p=ggplot(data=ggdf_p,mapping = aes(x=x,y=p,group=estimation))+geom_line(colour = "grey",alpha=0.7)+geom_line(data=ggdf_p%>%filter(estimation=="true"),mapping = aes(x=x,y=p))+ggtitle("Gamma(2,0.4)[0,10]+Delta_0,10+Poisson")#+ggtitle("Gamma(2,0.4)[0,10]+Delta_10+Poisson")

print(plotme_f)
print(plotme_p)
return(res[inds,])
}
```

```{r}
tic=proc.time()
pi_2p=PR_GP2P(Xs_bn=Xs_bn,a=0,b=10,theta0 = c(0.00001,10),nGQ=20,ntheta=100)
toc=proc.time()
toc-tic


apply(pi_2p,1,summary)
(pi_2p[1,]<0.25)%>%mean(.)
(pi_2p[2,]<0.25)%>%mean(.)
hist(pi_2p[1,])
hist(pi_2p[2,])
```


## Permutation Version PPR

```{r}
PPR_GPP=function(Xs_bn,a,b,theta0,nGQ,ntheta){

#permutation
N=nrow(Xs_bn)
n=ncol(Xs_bn)
nP=100
ind=sapply(1:nP,function(x){sample.int(n = n,size = n,replace = FALSE)})

#guass.quad
out=gauss.quad(nGQ)
xs_gq=out$nodes*(b-a)/2+(a+b)/2 #change interval
theta=seq(a,b,length.out = ntheta)

## Initial Guess: Uniform on [0,10]
p=rep(1/(b-a)/2,ntheta)
#p=dbeta(x = seq(0,1,length.out = ntheta),shape1 = c,shape2 = c)/(b-a)/2
inds=ceiling((theta0-a)/((b-a)/ntheta))

p[inds]=c(0.25,0.25)
## weight seq
w=1/(1:n+1)

##Recursion
ppr=function(i,p_0,Xs_bn){
  p=p_0
  xs_bn=Xs_bn[i,]
  Xs_bn_p=sapply(1:nP,function(i){xs_bn[ind[,i]]})

  pp=sapply(1:nP,function(ix){
    for (j in 1:n){
      p_x=map_dbl(theta,~dpois(x = Xs_bn_p[j,ix],lambda = .x))
      int=((b-a)/2*sum(out$weights*map_dbl(xs_gq,~dpois(x = Xs_bn_p[j,ix],lambda = .x))*p[ceiling(xs_gq/((b-a)/ntheta))])*(1-sum(p[inds])))+p[inds[1]]*dpois(x = Xs_bn_p[j,ix],lambda = theta0[1])+p[inds[2]]*dpois(x = Xs_bn_p[j,ix],lambda = theta0[2])
  p=(1-w[j])*p+w[j]*p_x*p/int

    }
    return(p)
  })%>%apply(., 1,mean)
  return(pp)
}

res=sapply(1:N,function(i){return(ppr(i,p,Xs_bn))})

##draw f(theta)
colnames(res)=paste0("est",1:N)
true_f=dtgamma(x_ = theta,shape_ = 2,rate_=0.4,a = a,b=b)*0.5
true_f[inds]=c(0.25,0.25)
res_f=res
for (col in 1:ncol(res)){
  res_f[-inds,col]=(1-sum(res[inds,col]))*res[-inds,col]
}
ggdf=res_f%>%as_tibble()%>%
  mutate(x=theta,true=true_f)%>%
  gather(data = .,key=estimation,value=p,-x)
plotme_f=ggplot(data=ggdf,mapping = aes(x=x,y=p,group=estimation))+geom_line(colour = "grey",alpha=0.7)+geom_line(data=ggdf%>%filter(estimation=="true"),mapping = aes(x=x,y=p))+ggtitle("Gamma(2,0.4)[0,10]+Delta_0,10+Poisson")


## get the p(x) -- Using Guassian Quadratic

Xss=apply(Xs_bn, 1, function(x){x_range(xs_vec = x,ntheta = ntheta,l = 0,u = Inf)})

xs=sapply(1:ntheta,function(j){
  map_dbl(.x = Xss[,j],.f = function(xs_j){
    (b-a)/2*sum(out$weights*map_dbl(xs_gq,~dpois(x=round(xs_j),lambda = .x))*res[,j][ceiling(xs_gq/((b-a)/ntheta))])*(1-sum(res[,j][inds]))+res[,j][inds[1]]*dpois(x = round(xs_j),lambda = theta0[1])+res[,j][inds[2]]*dpois(x = round(xs_j),lambda = theta0[2])
  })
  
})

true_xs=x_range(xs_vec = as.vector(Xs_bn),ntheta = ntheta,l = 0,u = Inf)
true=map_dbl(.x = true_xs,
             .f =function(xxs_i){ p=(b-a)/2*sum(out$weights*map_dbl(xs_gq,~dpois(x = round(xxs_i),lambda = .x))*(dtgamma(x_ = theta,shape_ = 2,rate_ = 0.4,a = a,b = b))[ceiling(xs_gq/((b-a)/ntheta))])*0.5+0.25*dpois(x = round(xxs_i),lambda = theta0[1])+0.25*dpois(x = round(xxs_i),lambda = theta0[2])
             })

ggdf_p=data_frame(x=c(as.vector(Xss),true_xs)%>%round(.),p=c(as.vector(xs),true),estimation=c(paste0("est",rep(1:N,each=ntheta)),rep("true",ntheta)))
plotme_p=ggplot(data=ggdf_p,mapping = aes(x=x,y=p,group=estimation))+geom_line(colour = "grey",alpha=0.7)+geom_line(data=ggdf_p%>%filter(estimation=="true"),mapping = aes(x=x,y=p))+ggtitle("Gamma(2,0.4)[0,10]+Delta_0,10+Poisson")

print(plotme_f)
print(plotme_p)
return(res[inds,])
}
```

```{r}
tic=proc.time()
pi__2p=PPR_GPP(Xs_bn=Xs_bn,a=0,b=10,theta0 = c(0.000001,10),nGQ=20,ntheta=100)
toc=proc.time()
toc-tic

```


```{r}
apply(pi__2p,1,summary)
(pi__2p[1,]<0.25)%>%mean(.)
(pi__2p[2,]<0.25)%>%mean(.)
hist(pi__2p[1,])
hist(pi__2p[2,])
```

